### 2020-04-15 probabilisticProgrammingMartingales.tex
Measurability of Rch(M) and related.

The one-step reduction is given by the function $\red : \Lambda \times S \to \Lambda \times S$ where
\begin{equation}
\red(M,s) = \left\{
    \begin{array}{ll}
        (E[N],s) & \text{if } M = E[R], R \to N \text{ and } R \neq \tsample \\
        (E[\underline{\pi_h(s)}],\pi_t(s)) & \text{if } M = E[\tsample] \\
        (M,s) & \text{if } M \text{ normal form}
    \end{array} \right .
\end{equation}

@@

For example, the term $(\tY \lambda f, n: \tif{\tsample - 0.5 < 0}{n}{f (n+1)} ) \underline{0}$, which generates a geometric distribution, terminates on the set $S \setminus [0.5,1]^\mathbb N$, which has measure 1, therefore it terminates almost surely, whereas $\tif{\tsample - 0.5 < 0}{\underline 0}{(\tY \lambda x. x) \underline 0}$, which terminates on the set $\pi_h^{-1}[[0,0.5]]$, has probability 0.5 of failing to terminate.

@@

@@

    \lo{I assume you mean $\int_{I} \mathsf{Leb} (\mathrm{d} x) \, f(E[\underline{x}])$.}

    \akr{Is the meaning of the integral unclear in the context? I'm not sure whether $Rch(M)$ is a measurable subset of $\Lambda$, so it might not have a natural measure, but I'm pretty sure this doesn't actually matter, and the $\sigma$-algebra at least is well-defined. $Rch(M)$ could fail to be measurable if there are measurable functions $\mathbb R^n \to \mathbb R$ with non-measurable ranges. I don't know whether these exist. They do for the Lebesgue $\sigma$-algebra, but I'm using the Borel ones.}
    \lo{For the integral to be well-defined, we need $x \mapsto E[\underline x]$ to be a measurable function $\mathbb{R} \to \mathit{Rch}(M)$ (I am sure it is, assuming an appropriate definition of SPCF terms as a measurable space.).}

>>>>

The one-step reduction, \changed[lo]{$\to$}, is given by the function $\red : \Lambda \times S \to \Lambda \times S$ where
\begin{equation}
\red(M,s) = \left\{
    \begin{array}{ll}
        (E[N],s) & \text{if } M = E[R], R \to N \text{ and } R \neq \tsample \\
        (E[\underline{\pi_h(s)}],\pi_t(s)) & \text{if } M = E[\tsample] \\
        (M,s) & \text{if } M \text{ normal form}
    \end{array} \right .
\end{equation}

@@

For example, the term $(\tY \lambda f, n: \tif{\tsample - 0.5 < 0}{n}{f (n+1)} ) \, \underline{0}$, which generates a geometric distribution, terminates on the set $S \setminus [0.5,1]^\mathbb N$, which has measure 1, therefore it terminates almost surely, whereas $\tif{\tsample - 0.5 < 0}{\underline 0}{(\tY \lambda x. x) \underline 0}$, which terminates on the set $\pi_h^{-1}[[0,0.5]]$, has probability 0.5 of failing to terminate.

@@

\lo{Your operational semantics does not maintain a record of the current weight of the reduction.
Note that a.s.~termination does depend on $\tscore$: see \cite[\S 4.3]{DBLP:journals/corr/abs-2004-03924}\footnote{\url{https://arxiv.org/abs/2004.03924}}.}

@@

    \lo{I agree that it does not actually matter whether $\mathit{Rch}(M)$ is a measurable subset of $\Lambda$ (the set of SPCF terms).}

    \lo{It is straightforward to see that $E[\cdot] : x \mapsto E[\underline x]$ is a measurable function $\mathbb{R} \to \mathit{Rch}(M)$, using the ``skeletal term'' $\sigma$-algebra on $\mathit{Rch}(M)$, and so, $x \mapsto f(E[\underline{x}])$ is measurable.}

    \lo{I assume you mean $\int_{I} \mathsf{Leb} (\mathrm{d} x) \, f(E[\underline{x}])$.} 
    \akr{Is the meaning of the integral unclear in the context?} 
    \lo{It it -- I was being pedantic. What you write is a Riemann integral, but it coincides with Lebesgue in this case.}

    \akr{I'm not sure whether $Rch(M)$ is a measurable subset of $\Lambda$, so it might not have a natural measure, but I'm pretty sure this doesn't actually matter, and the $\sigma$-algebra at least is well-defined. $Rch(M)$ could fail to be measurable if there are measurable functions $\mathbb R^n \to \mathbb R$ with non-measurable ranges. I don't know whether these exist. They do for the Lebesgue $\sigma$-algebra, but I'm using the Borel ones.}
    \lo{For the integral to be well-defined, we need $x \mapsto E[\underline x]$ to be a measurable function $\mathbb{R} \to \mathit{Rch}(M)$ (I am sure it is, assuming an appropriate definition of SPCF terms as a measurable space.).}
